---
title: "big data class 2020"
author: "Juan Vazquez"
date: "May 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Week 01

* MongoDB explanation in [5 minutes](https://www.youtube.com/watch?v=EE8ZTQxa0AM).

* [MongoDB Atlas](https://docs.atlas.mongodb.com/getting-started/)
* [SQL comparison](https://docs.mongodb.com/manual/reference/sql-comparison/)
* [mongo shell methods](https://docs.mongodb.com/manual/reference/method/)

For bugs updating from mongoDB 3.6 to 4.2 [1](https://stackoverflow.com/questions/34733340/mongodb-gpg-invalid-signatures) and [2](https://futurestud.io/tutorials/fix-ubuntu-debian-apt-get-keyexpired-the-following-signatures-were-invalid).


### Week 02

[MongoDB sample datasets](https://docs.atlas.mongodb.com/sample-data/available-sample-datasets/)
[atlas sample queries](https://docs.atlas.mongodb.com/reference/atlas-search/tutorial/)

Software to Install [docker](https://docs.docker.com/engine/install/) ¿cómo correrlo en las 3 plataformas?


### Week 03

Hadoop links [free online training](https://community.cloudera.com/t5/Support-Questions/I-have-to-practise-hadoop-hive-pig-sqoop-oozie-map-reduce/td-p/154089), [AWS](https://us-east-2.console.aws.amazon.com/console/home?nc2=h_ct&region=us-east-2&src=header-signin#), [quora](https://www.quora.com/How-can-I-practice-Hadoop-programs-online-for-free-Is-there-any-free-cloud-service-that-provides-Hadoop-platform-along-with-sample-data-to-play-with-I-want-to-submit-map-reduce-code-there-and-get-the-results-Is-there-any-such-service-available), [docker](https://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/DockerContainers.html).

[cassandra](https://cassandra.apache.org/doc/latest/getting_started/index.html)

* [big data vs data science](https://scontent.fcjs3-2.fna.fbcdn.net/v/t1.0-9/fr/cp0/e15/q65/98196020_2936124596468271_8768436709881806848_o.jpg?_nc_cat=101&_nc_sid=ca434c&efg=eyJpIjoidCJ9&_nc_eui2=AeGAu1fDicKVRbD5wpxrJimaJvsLtw3bj7om-wu3DduPuq_e0F8k2AjtZZWVw1vk70w&_nc_ohc=Vi2rkUAHVBwAX89Phr5&_nc_ht=scontent.fcjs3-2.fna&_nc_tp=14&oh=681cfad4fa23af2d9dee4e267c760280&oe=5EEA6C37)

#### Class 2

* [landscape of big data technologies 2019](http://mattturck.com/wp-content/uploads/2019/07/2019_Matt_Turck_Big_Data_Landscape_Final_Fullsize.png) via [matturck](https://mattturck.com/data2019/).
list of technologies
* [datadog](https://www.datadoghq.com/product/)

#### Class 3

*  [JSON datasets](https://github.com/jdorfman/awesome-json-datasets#nobel-prize)


### Week 04

* [Datos censales](https://abxda.wordpress.com/2020/03/18/geo-big-data-con-datos-censales/) y [datalake](https://abxda.wordpress.com/2020/05/06/analizando-el-big-data-de-las-noticias-con-tu-micro-data-lake-baterias-incluidas/) con tecnologías como Docker y Spark por Abel Coronado Iruegas


* Discuss [human face of big data](https://www.youtube.com/watch?v=4VeITe6EJDU) and its impact with coronavirus, like the failure of machine learning algorithms of predictive models of shoping.

Book lists [1](https://solutionsreview.com/data-management/top-25-best-big-data-books-on-amazon-you-should-read/) and [2](https://www.goodreads.com/shelf/show/big-data).


#### class 3

NoSQL database comparisons

* [social compare](https://socialcompare.com/en/comparison/nosql-databases-solution-cassandra-mongodb-couchdb)
* [logz](https://logz.io/blog/nosql-database-comparison/)
* [Action labs](https://www.accionlabs.com/articles/2018/4/9/choosing-a-nosql-database-technology-comparison-matrix)
* [Digital ocean](https://www.digitalocean.com/community/tutorials/a-comparison-of-nosql-database-management-systems-and-models)



### Week 05

Stanford [course](https://www.cis.upenn.edu/~susan/cis700/syllabus.html).

### DOCKER class

* [play with docker](https://labs.play-with-docker.com/), [classroom](https://training.play-with-docker.com/alacart/) and [training](https://training.play-with-docker.com/).

https://codeshare.io/ambnBX

```{r eval=FALSE, echo=TRUE}
# 1. pull docker image
sudo docker pull kiwenlau/hadoop:1.0

# 2. clone github repository
git clone https://github.com/kiwenlau/hadoop-cluster-docker

3. create hadoop network
sudo docker network create --driver=bridge hadoop

#acompleten plis
sudo ./start-cointainers


wget https://examplebenjamin.s3.amazonaws.com/data.zip

hdfs dfs –mkdir –p /user/rawdata/netflix
hdfs dfs –put data.zip /user/rawdata/netflix
hdfs dfs –ls  /user/rawdata/netflix
hdfs dfs –cat /user/rawdata/netflix
hdfs dfs –rm –f /user/rawdata/netflix


# 4. start container
cd hadoop-cluster-docker
sudo ./start-container.sh

output:
start hadoop-master container...
start hadoop-slave1 container...
start hadoop-slave2 container...
root@hadoop-master:~# 

# 5. start hadoop
./start-hadoop.sh

# 6. run wordcount
./run-wordcount.sh
```

References [hadoop](https://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/DockerContainers.html).
[Hadoop in docker](https://clubhouse.io/developer-how-to/how-to-set-up-a-hadoop-cluster-in-docker/).

class 3

* [SOLID](https://medium.com/@mari_azevedo/s-o-l-i-d-principles-what-are-they-and-why-projects-should-use-them-50b85e4aa8b6).

### Week 06

#### Class 1

NoSQL [Wikipedia](https://en.wikipedia.org/wiki/NoSQL)
Paper de comparación de [NoSQL DB](https://www.researchgate.net/publication/278963532_Comparison_and_Classification_of_NoSQL_Databases_for_Big_Data)


AWS on [local](https://github.com/localstack/localstack). 

HDFS and hadoop fs links [1](https://www.thomashenson.com/hadoop-fs-commands/), [2](https://www.geeksforgeeks.org/hdfs-commands/), [3](https://data-flair.training/blogs/top-hadoop-hdfs-commands-tutorial/).


#### class 2

* [hadoop cheatsheet](https://images.linoxide.com/hadoop-hdfs-commands-cheatsheet.pdf).
* [another docker way to mount](https://www.youtube.com/watch?v=Ho_gcZpzeqk).

#### class 3

word count
* [mapreduce in python](https://www.michael-noll.com/tutorials/writing-an-hadoop-mapreduce-program-in-python/)
* [another example](https://towardsdatascience.com/a-beginners-introduction-into-mapreduce-2c912bb5e6ac)

* mention [continuous integration](https://circleci.com/continuous-integration/)

#### RDDs

* [some notes](http://www.mikelnino.com/2016/03/claves-principales-resilient-distributed-datasets-rdd-apache-spark.html)

* [pyspark mapreduce example](https://annefou.github.io/pyspark/02-mapreduce/)


### Week 07

#### class 1, spark MLlib

* [Scikit-Learn](https://scikit-learn.org/stable/tutorial/machine_learning_map/index.html)
* [MLlib reference](https://spark.apache.org/docs/latest/ml-guide.html).
* [Precision & recall](https://pair.withgoogle.com/chapter/user-needs/).
* [bias-variance tradeoff](http://www.r2d3.us/visual-intro-to-machine-learning-part-2/).
* Revisar para mayor profundidad el libro de Hands on Machine Learning with scikit-learn, keras and tensorflow de Aurelien Geron.
* H2O+ SPARK = [Sparkling water](https://www.h2o.ai/products/h2o-sparkling-water/).






### Week 08
### Week 09
### Week 10
### Week 11
### Week 12
### Week 13

* [grafana](https://grafana.com/blog/2020/05/18/grafana-v7.0-released-new-plugin-architecture-visualizations-transformations-native-trace-support-and-more/?isource=hp)


https://www.cloudera.com/downloads/hortonworks-sandbox.html



## R Markdown

[latex online editor ](https://latexbase.com/d/ea22422c-dee8-4428-8764-3a16a831cbab) and
[bookdown](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#text-references) is a framework to deliver books.

### Spark streaming and kafka

some guides [post1](https://mapr.com/blog/quick-guide-spark-streaming/) and [post2](https://databricks.com/glossary/what-is-spark-streaming)


